%----------------------------------------------------------------------------------------
%	SECTION TITLE
%----------------------------------------------------------------------------------------

\cvsection{Experience}

%----------------------------------------------------------------------------------------
%	SECTION CONTENT
%----------------------------------------------------------------------------------------

\begin{cventries}

%------------------------------------------------

\cventry
{Senior Software Engineer} % Job title
{The MathWorks, Inc.} % Organization
{Natick, Massachusetts} % Location
{Nov. 2013 - Present} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {Designed, implemented, tested, and documented initial version of the Simscape Fluids 1.0 fluid modelling library for Simscape. This library is used by many leading engineering companies in their design workflows.}
\item {Led project to convert many hydraulic components to new isothermal library, leading to 40\% improved performance and much improved accuracy.}
\item {Presented technical details of libraries and features at industry conference before hundreds of attendees.}
\item{Worked with external business industry contacts to include new functionalities including the built-in fluids properties in Simscape Fluids libraries.\\}
\end{cvitems}
}

 %------------------------------------------------    

\cventry
{Research Associate} % Job title
{PerkinElmer Health Sciences Canada, Inc.} % Organization
{Woodbridge, Ontario, Canada} % Location
{Jun. 2012 - May. 2013} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {Developed a computational model of magneto-hydrodynamics (MHD) and particle transport in mass spectrometry technology to identify the main factors in design optimization. Worked directly with the chief technology scientist and the director of R\&D.}
\item {Work led to an innovative experimental initiative to develop the next-generation of spray injectors
to increase the evaporation efficiency of aerosols in mass spectrometry instruments.}
\item{Prepared technical reports and presented the results in American Association for Aerosol Research (AAAR) conference and European Winter Conference on Plasma Spectrochemistry (EWCPS).\\}
\end{cvitems}
}

%------------------------------------------------

\cventry
{Research Assistant} % Job title
{Centre for Advancing Coating and Technology (CACT), University of Toronto} % Organization
{Toronto, Ontario, Canada} % Location
{Jan. 2006 - April. 2013} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {Created a computational platform for design and optimization of the process of carbon nanotube
production by radio frequency inductively coupled plasma (RF-ICP) technology.}
\item {Identified the limiting factors in the yield rate of carbon nanotubes in RF-ICP technology and
developed a computational model to analyze the fluid flow and heat transfer in the system's initial re-design development.}
\item{Conducted design validations of a chemical kinetic model for predicting the chemistry of generated nanoparticles and nanomaterial in the RF-ICP system through optimized parallel-computing
implementations in an in-house CFD software.}
\end{cvitems} 
}

%------------------------------------------------

%\cventry
%{Visiting Worker} % Job title
%{MNA- Molecular and Nanomaterials Architecture Group, Steacie Institute for Molecular
%Sciences (SIMS), National Research Council of Canada,} % Organization
%{Ottawa, Canada} % Location
%{Jan. 2011 - Mar. 2011} % Date(s)
%{ % Description(s) of tasks/responsibilities
%\begin{cvitems}
%\item {Visited the experimental facilities of carbon nanotube production by RF-ICP technology to trans-
%late the essential aspects of the operating conditions in the experiments into the predicting computational model.}
%\item{Organized technical meetings with the research scientists and presented the progress report on
%the computational results in the internal meetings.}
%\end{cvitems}
%}

%------------------------------------------------

%\cventry
%{Research Assistant} % Job title
%{Multiphase Flow and Thermal Spray Laboratories, Concordia University} % Organization
%{Montreal, Quebec, Canada} % Location
%{Sep. 2005 - Dec. 2007} % Date(s)
%{ % Description(s) of tasks/responsibilities
%\begin{cvitems}
%\item {Identified the effect of nanoparticle suspension solutions on liquid spray characteristics in thermal
%spray coating applications.}
%\item{Developed a computational model of the two-phase flow in an effervescent atomizer for nano-suspension spray technologies.}
%\end{cvitems}
%}

%------------------------------------------------

%\cventry
%{Design Engineer} % Job title
%{Karandishan Engineering Consultant Co.} % Organization
%{Tehran, Iran} % Location
%{Jul. 2003 - Aug. 2005} % Date(s)
%{ % Description(s) of tasks/responsibilities
%\begin{cvitems}
%\item {Conducted research on designing solar energy systems in photovoltaic and thermal systems.}
%\end{cvitems}
%}

%------------------------------------------------

\end{cventries}