%----------------------------------------------------------------------------------------
%	SECTION TITLE
%----------------------------------------------------------------------------------------

\cvsection{Publications}

%----------------------------------------------------------------------------------------
%	SECTION CONTENT
%----------------------------------------------------------------------------------------

\begin{cventries}

%------------------------------------------------

\cventry
{} % Role
{Book Chapters} % Title
{} % Location
{} % Date(s)
{ % Description(s)
\vspace{-3 mm}
\begin{cvitems}
\item {S. Arabzadeh Esfarjani, Numerical Simulation of Two-phase Flow in an Effervescent Atomizer, VDM Verlag Dr. Mller Publication.}
\item {S. Arabzadeh Esfarjani, Heating and Cooling load calculations Chapters, Applied Energy
Saving Handbook, T. Fatanat Didar (ed), Sharif University publications, Tehran (2006).
(The first practical handbook on energy saving in Iran).\\}
\end{cvitems}
}

%------------------------------------------------

\cventry
{} % Role
{Peer-Reviewed Publications} % Title
{} % Location
{} % Date(s)
{ % Description(s)
\vspace{-3 mm}
\begin{cvitems}
\item {S. Arabzadeh Esfarjani, S. B. Dworkin, J. Mostaghimi, K. S. Kim, C. T. Kingston, B. Simard,
and G. Soucy, "Detailed Numerical Simulation of Single-Walled Carbon Nanotube Synthesis in a
Radio-Frequency Induction Thermal Plasma System", Journal of Physics Conference Series, 406
(2012) 012011.}
\item{S. Arabzadeh Esfarjani, J. Mostaghimi, K. Kim, A. Shahverdi, and G. Soucy, "Radio Frequency Thermal Plasma: The Cutting Edge Technology in Production of Single-Walled Carbon Nanotubes", Journal of Thermal Science and Technology, 6 (2011) 307-322.}
\item {S. Arabzadeh Esfarjani, and A. Dolatabadi, "A 3D Simulation of Two-phase Flow in an Effervescent Atomizer for Suspension Plasma spray", Surface and Coatings Technology, 203 (2008) 2074-2080.}
\item{S. Arabzadeh Esfarjani, and A. Dolatabadi, "Numerical Simulation of Nano-Particle Suspension in an Effervescent Atomizer", Journal of Computational and Theoretical Nanoscience, 5(2008) 1-8.\\}
\end{cvitems}
}

%------------------------------------------------
\cventry
{} % Role
{Conference Proceedings and Presentations} % Title
{} % Location
{} % Date(s)
{ % Description(s)
\vspace{-3 mm}
\begin{cvitems}
\item {"A Piezoelectrically Actuated Nebulizer for Inductively Coupled Plasma Mass Spectrometry
(ICP-MS)", S. Arabzadeh Esfarjani, H. R. Badiei, K. Kahen, and J. Mostaghimi, 31st American Association for Aerosol Research (AAAR) Annual Conference, Minnesota, USA, 8-12 October
2012.}
\item{"Detailed Numerical Simulation of Single-Walled Carbon Nanotube Synthesis in a Radio-Frequency Induction Thermal Plasma System", S. Arabzadeh Esfarjani, S. B. Dworkin, J. Mostaghimi, K. S. Kim, C. T. Kingston, B. Simard, and G. Soucy, 12th High-Tech Plasma Processes Conference (HTPP-12), Bologna, Italy, 24-29 June 2012.}
\item {"Parametric Study of Thermo-Flow Fields in an Inductively Coupled RF Plasma Processing
System for the Production of Single-Walled Carbon Nanotubes", S. Arabzadeh Esfarjani, J.
Mostaghimi, A. Shahverdi, G. Soucy, K. S. Kim, and B. Simard, 20th International Symposium
on Plasma Chemistry (ISPC20), Philadelphia, USA, 24-29 July 2011.}
\item{"CFD Simulation of Single-walled Carbon Nanotube Growth in an RF Induction Thermal Plasma Process with Chemistry Model", S. Arabzadeh Esfarjani, S. B. Dworkin, J. Mostaghimi, K. S. Kim, B. Simard, and G. Soucy, 42nd AIAA Plasma dynamics and Lasers Conference in conjunction with the 18th International Conference on MHD Energy Conversion (ICMHD), Honolulu, Hawaii, USA, 27 - 30 Jun 2011.}
\item{"Simulation of Single-walled CNT Growth in an RF Induction Thermal Plasma Process with
a Detailed Chemistry-Particulate Model", S. Arabzadeh Esfarjani, S. B. Dworkin, and J.
Mostaghimi, SIMS-NRC strategic meeting, Ottawa, Ontario, Canada, 6 December 2010.}
%\item{"In situ Purity Enhancement and Surface Modification of Single-Walled carbon Nanotubes Synthesized by Induction Thermal Plasma", A. Shahverdi, K. Kim, Y. Alinejad, S. Arabzadeh
%Esfarjani, J. Mostaghimi, and G. Soucy, NT10 Eleventh International Conference on the Science and Application of Nanotubes, Montreal, Quebec, Canada, June 27-July 2, 2010.}
%\item{"Reactive Flows and Vortices", S. Arabzadeh Esfarjani, A. Bourlioux, A. D. Foucault, P.
%Gauthier, A. Majumdar, C. Mavriplis, M. M. Ramirez, S. Peppin, M. Pugh, L.X. Proulx, T.
%Reis, N. Shahbazian, Third Montreal Industrial Problem Solving Workshop, MITACS, Centre de
%Recherches Mathematiques, Universite de Montreal, August 17 - 21 2009.}
%\item{"A 3D Simulation of Two-phase Flow in an Effervescent Atomizer for Suspension Plasma spray", S. Arabzadeh Esfarjani, and A. Dolatabadi, Proceedings of 2nd International Workshop on Suspension and Solution Thermal Spraying (S2TS), Tours, France, June 5-7, 2008.}
\end{cvitems}
}

\end{cventries}